quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-18 paper-quollr.Rmd
Updated section Computing hexagon grid configurations

#### Computing hexagon grid configurations

The configurations of a hexagonal grid are determined by the number of bins and the bin width in each direction. The function `calc_bins_y()` is used for this purpose. This function accepts (1) an object (`nldr_scaled_obj`) containing three elements: the first is the scaled NLDR data (`scaled_nldr`), and the second and third are the limits of the original NLDR data (`lim1` and `lim2`); (2) the number of bins along the x-axis (`b1`), and (3) the buffer amount as a proportion (`q`). The buffer ensures that the grid fully covers the data space by extending one hexagon width ($a_1$) and height ($a_2$) beyond the observed data in all directions. By default, $q = 0.1$, but it must be set to a value smaller than the minimum data value to avoid exceeding the data range.

>>>>

#### Computing hexagon grid configuration

The function `calc_bins_y()` determines the configuration of the hexagonal grid by computing the number of bins along the y-axis (`b2`), the hexagon width (`a1`), and height (`a2`). This function accepts (1) an object (`nldr_scaled_obj`) containing three elements: the first is the scaled NLDR data (`scaled_nldr`), and the second and third are the limits of the original NLDR data (`lim1` and `lim2`); (2) the number of bins along the x-axis (`b1`), and (3) the buffer amount as a proportion (`q`). The buffer ensures that the grid fully covers the data space by extending one hexagon width ($a_1$) and height ($a_2$) beyond the observed data in all directions. By default, $q = 0.1$, but it must be set to a value smaller than the minimum data value to avoid exceeding the data range.

### 2025-09-18 paper-quollr.tex
Updated section Computing hexagon grid configurations

\paragraph{Computing hexagon grid configurations}\label{computing-hexagon-grid-configurations}

The configurations of a hexagonal grid are determined by the number of bins and the bin width in each direction. The function \texttt{calc\_bins\_y()} is used for this purpose. This function accepts (1) an object (\texttt{nldr\_scaled\_obj}) containing three elements: the first is the scaled NLDR data (\texttt{scaled\_nldr}), and the second and third are the limits of the original NLDR data (\texttt{lim1} and \texttt{lim2}); (2) the number of bins along the x-axis (\texttt{b1}), and (3) the buffer amount as a proportion (\texttt{q}). The buffer ensures that the grid fully covers the data space by extending one hexagon width (\(a_1\)) and height (\(a_2\)) beyond the observed data in all directions. By default, \(q = 0.1\), but it must be set to a value smaller than the minimum data value to avoid exceeding the data range.

>>>>

\paragraph{Computing hexagon grid configuration}\label{computing-hexagon-grid-configuration}

The function \texttt{calc\_bins\_y()} determines the configuration of the hexagonal grid by computing the number of bins along the y-axis (\texttt{b2}), the hexagon width (\texttt{a1}), and height (\texttt{a2}). This function accepts (1) an object (\texttt{nldr\_scaled\_obj}) containing three elements: the first is the scaled NLDR data (\texttt{scaled\_nldr}), and the second and third are the limits of the original NLDR data (\texttt{lim1} and \texttt{lim2}); (2) the number of bins along the x-axis (\texttt{b1}), and (3) the buffer amount as a proportion (\texttt{q}). The buffer ensures that the grid fully covers the data space by extending one hexagon width (\(a_1\)) and height (\(a_2\)) beyond the observed data in all directions. By default, \(q = 0.1\), but it must be set to a value smaller than the minimum data value to avoid exceeding the data range.
